---
title: "Creating Desktop Notifier in R"
output: html_notebook
author: Anish Singh Walia
---

-------------




#### In this tutorial we are going to create a desktop notifier using R and [Notifier](https://github.com/gaborcsardi/notifier) package.Notifier package is available on Github and below is the method to download and install a package from Github.

```{r warning=FALSE,message=FALSE}

#install.packages("devtools") if devtools is not installed
devtools::install_github("gaborcsardi/notifier")
install.packages("randquotes")
install.packages("beepr")

library(notifier)
library(rvest)
library(randquotes)
library(janitor)

#for notification sounds
require(beepr)


```


#### How does Notifier works ?

a) __MAC OS__ : It uses MAC's terminal-Notifier tool(https://github.com/julienXX/terminal-notifier).


b) __Linux based and BSD based systems__:It Notify-send command line tool is used. This requires the libnotify-bin package on Ubuntu/Debian and similar systems, or the libnotify package on RedHat/CentOS/Fedora and similar systems.

c) __Windows__: Windows versions, notifier uses the toaster tool, see https://github.com/nels-o/toaster.


----------------



#### Usage of Notifier

__"notifier"__ uses one basic function to create a notification or as the function says, “notify“. The function notify() takes the below three arguments:

a) title — Message title.

b) msg — Actual Notification Message.

c) image — Image, along with the message — optional.


```{r warning=FALSE,message=FALSE}

##making the first notification message

notify(
  title = "World Clock",
  msg= c(
    paste0(" India - ", format(Sys.time(), format = "%H:%M:%S" ,tz = "Asia/Calcutta"),"\n",
                 paste0("Singapore - ", format(Sys.time(), format = "%H:%M:%S" ,tz = "Asia/Singapore"),"\n"))
  )
)


```



#### Making a notifier which will send notifications after regular Intervals:

There are multiple use cases for the desktop notifications for example you want to get notified every time the script gets completed.

```{r warning=FALSE,message=FALSE}


# making a function to send notifications every 1 minute

repeat {
  
  # getting the current time
  startTime <- Sys.time() 
  
  
  notify(
    
    title = "Quote of the Day",
    msg = c(randquote_simple())
)

  #repead
  sleepTime <- startTime + 60 - Sys.time()
  if (sleepTime > 0)
  Sys.sleep(sleepTime)

  
}


```


#### Making a notifier which sends COVID-19 cases summary for India

Let's first get the data from the data source. Here you can scrape data from any source in R. The process is fairly simple. A good post on scraping data in in R using a really good package [rvest](r-bloggers.com/using-rvest-to-scrape-an-html-table/)


```{r message=FALSE,warning=FALSE}

 myfile1 <- getURL('https://api.covid19india.org/csv/latest/state_wise.csv', 
                    ssl.verifyhost=FALSE, ssl.verifypeer=FALSE)
  
  #dataset with summariesed case counts of statese
  StateCOVID_19 <- read.csv(textConnection(myfile1), header=T)

 msg1 <- paste("Confirmed Cases: ",Confirmed,", Revovered:",Recovered)
 msg2<-  paste("Deaths: ",Deaths, ", Active:\n ",Active)
 msg3 <- paste(StateCOVID_19[2,2],"\nConfirmed:",StateCOVID_19[2,3],",", "Recovered:  ",StateCOVID_19[2,4],",\n", "Deaths:  ",StateCOVID_19[2,5], ",", "Active: ",StateCOVID_19[2,6])

 
repeat {
  
  # getting the current time
  startTime <- Sys.time() 
  
  
  notify(
    
    title = "COVID-19 India Summary",
    msg = c(msg1,msg2,msg3)
)
  
  #adding the beep notification sound
   beep("wilhelm")

  #repeat
  sleepTime <- startTime + 60 - Sys.time()
  if (sleepTime > 0)
  Sys.sleep(sleepTime)

  
}
 



```





