---
title: "Creating Desktop Notifier in R"
output: html_notebook
author: Anish Singh Walia
---

-------------




#### In this tutorial we are going to create a desktop notifier using R and [Notifier](https://github.com/gaborcsardi/notifier) package.Notifier package is available on Github and below is the method to download and install a package from Github.

```{r warning=FALSE,message=FALSE}

#install.packages("devtools") if devtools is not installed
devtools::install_github("gaborcsardi/notifier")
install.packages("randquotes")
install.packages("beepr")

library(notifier)
library(rvest)
library(randquotes)
library(janitor)

#for notification sounds
require(beepr)


```


#### How does Notifier works ?

a) __MAC OS__ : It uses MAC's terminal-Notifier tool(https://github.com/julienXX/terminal-notifier).


b) __Linux based and BSD based systems__:It Notify-send command line tool is used. This requires the libnotify-bin package on Ubuntu/Debian and similar systems, or the libnotify package on RedHat/CentOS/Fedora and similar systems.

c) __Windows__: Windows versions, notifier uses the toaster tool, see https://github.com/nels-o/toaster.


----------------



#### Usage of Notifier

__"notifier"__ uses one basic function to create a notification or as the function says, “notify“. The function notify() takes the below three arguments:

a) title — Message title.

b) msg — Actual Notification Message.

c) image — Image, along with the message — optional.


```{r warning=FALSE,message=FALSE}

##making the first notification message

notify(
  title = "World Clock",
  msg= c(
    paste0(" India - ", format(Sys.time(), format = "%H:%M:%S" ,tz = "Asia/Calcutta"),"\n",
                 paste0("Singapore - ", format(Sys.time(), format = "%H:%M:%S" ,tz = "Asia/Singapore"),"\n"))
  )
)


```



#### Making a notifier which will send notifications after regular Intervals:

There are multiple use cases for the desktop notifications for example you want to get notified every time the script gets completed.

```{r warning=FALSE,message=FALSE}


# making a function to send notifications every 1 minute

repeat {
  
  # getting the current time
  startTime <- Sys.time() 
  
  
  notify(
    
    title = "Quote of the Day",
    msg = c(randquote_simple())
)

  #repead
  sleepTime <- startTime + 60 - Sys.time()
  if (sleepTime > 0)
  Sys.sleep(sleepTime)

  
}


```


#### Scraping a table using rvest

Let's try to get a HTML table and get notifed after regular intervals with a beep sound using [beepr](https://www.r-project.org/nosvn/pandoc/beepr.html). Here we can scrape a HTML table using [rvest](r-bloggers.com/using-rvest-to-scrape-an-html-table/) package.


```{r message=FALSE,warning=FALSE}

url_state <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSz8Qs1gE_IYpzlkFkCXGcL_BqR8hZieWVi-rphN1gfrO3H4lDtVZs4kd0C3P8Y9lhsT1rhoB-Q_cP4/pubhtml"



StateCOVID_19 <- url_state %>%
  read_html() %>%
  html_nodes(xpath='//*[@id="1896310216"]/div/table') %>%
  html_table()

StateCOVID_19 <- StateCOVID_19[[1]]  

#Setting 1 row as column names:
StateCOVID_19 <- StateCOVID_19 %>%  row_to_names(row_number = 1)

#removing column 1 as it is not necessary:
StateCOVID_19[,3] <- NA
StateCOVID_19 <-remove_empty(StateCOVID_19,"cols")
StateCOVID_19 <- na.omit(StateCOVID_19)



 Confirmed<- StateCOVID_19$Confirmed[1]
 Deaths <- StateCOVID_19$Deaths[1]
 Recovered <- StateCOVID_19$Recovered[1]
 Active <- StateCOVID_19$Active[1]

 msg1 <- paste("Confirmed Cases: ",Confirmed,", Revovered:",Recovered)
 msg2<-  paste("Deaths: ",Deaths, ", Active:\n ",Active)
 msg3 <- paste(StateCOVID_19[2,2],"\nConfirmed:",StateCOVID_19[2,3],",", "Recovered:  ",StateCOVID_19[2,4],",\n", "Deaths:  ",StateCOVID_19[2,5], ",", "Active: ",StateCOVID_19[2,6])

 
repeat {
  
  # getting the current time
  startTime <- Sys.time() 
  
  
  notify(
    
    title = "COVID-19 India Summary",
    msg = c(msg1,msg2,msg3)
)
  
  #adding the beep notification sound
  beep()

  #repeat
  sleepTime <- startTime + 60 - Sys.time()
  if (sleepTime > 0)
  Sys.sleep(sleepTime)

  
}
 
 


```





