---
title: "Creating Desktop Notifier in R"
output: html_notebook
author: Anish Singh Walia
---

-------------




#### In this tutorial we are going to create a desktop notifier using R and [Notifier](https://github.com/gaborcsardi/notifier) package.Notifier package is available on Github and below is the method to download and install a package from Github.

```{r warning=FALSE,message=FALSE}

#install.packages("devtools") if devtools is not installed
devtools::install_github("gaborcsardi/notifier")
install.packages("randquotes")
library(notifier)

library(randquotes)


```


#### How does Notifier works ?

a) __MAC OS__ : It uses MAC's terminal-Notifier tool(https://github.com/julienXX/terminal-notifier).


b) __Linux based and BSD based systems__:It Notify-send command line tool is used. This requires the libnotify-bin package on Ubuntu/Debian and similar systems, or the libnotify package on RedHat/CentOS/Fedora and similar systems.

c) __Windows__: Windows versions, notifier uses the toaster tool, see https://github.com/nels-o/toaster.


----------------



#### Usage of Notifier

__"notifier"__ uses one basic function to create a notification or as the function says, “notify“. The function notify() takes the below three arguments:

a) title — Message title.

b) msg — Actual Notification Message.

c) image — Image, along with the message — optional.


```{r warning=FALSE,message=FALSE}

##making the first notification message

notify(
  title = "World Clock",
  msg= c(
    paste0(" India - ", format(Sys.time(), format = "%H:%M:%S" ,tz = "Asia/Calcutta"),"\n",
                 paste0("Singapore - ", format(Sys.time(), format = "%H:%M:%S" ,tz = "Asia/Singapore"),"\n"))
  )
)


```



#### Making a notifier which will send notifications after regular Intervals:

There are multiple use cases for the desktop notifications for example you want to get notified every time the script gets completed.

```{r warning=FALSE,message=FALSE}


# making a function to send notifications every 1 minute

repeat {
  
  # getting the current time
  startTime <- Sys.time() 
  
  
  notify(
    
    title = "Quote of the Day",
    msg = c(randquote_simple())
)

  sleepTime <- startTime + 60 - Sys.time()
  if (sleepTime > 0)
  Sys.sleep(sleepTime)

  
}


```





